Eurovision **Dance** Contest 2008

### 2023-10-29 inst/eurodance.Rmd
label each chunk

```{r,cache=TRUE}
eurodance <- hyper2()
for(i in seq_len(ncol(pref))){
	x <- pref[,i]
	eurodance %<>% `+`(ordervec2supp(x[!is.na(x)]))
}  # i loop closes
eurodance_maxp <- maxp(eurodance)
eurodance_maxp
pie(eurodance_maxp)
```

@@

```{r,cache=TRUE}
consistency(eurodance)
```

@@

```{r}
(jj <- o[,2])
jj <- sort(jj,decreasing=TRUE)
jj[jj>0] <- seq_len(sum(jj>0))
jury <- jj
jury
```

@@

```{r,cache=TRUE}
n <- 4000
LL <- rep(0,n)
for(i in seq_len(n)){
	jjstar <- sample(jury)
	names(jjstar) <- names(jury)
	LL[i] <- loglik(indep(eurodance_maxp),ordervec2supp(jjstar),log=FALSE)
}
```

```{r}
plot(sort(LL),log="y")
p <- loglik(indep(eurodance_maxp),ordervec2supp(jury),log=FALSE)
abline(h=p)
```

```{r}
sum(LL[LL<p])/sum(LL)
```

>>>>

```{r,label=eachcolisorder,cache=TRUE}
eurodance <- hyper2()
for(i in seq_len(ncol(pref))){
	x <- pref[,i]
	eurodance %<>% `+`(ordervec2supp(x[!is.na(x)]))
}  # i loop closes
eurodance_maxp <- maxp(eurodance)
eurodance_maxp
pie(eurodance_maxp)
```

@@

```{r,label=verifyconsistency,cache=TRUE}
consistency(eurodance)
```

@@

```{r,label=considerjury}
(jj <- o[,2])
jj <- sort(jj,decreasing=TRUE)
jj[jj>0] <- seq_len(sum(jj>0))
jury <- jj
jury
```

@@

```{r,label=simfish,cache=TRUE}
n <- 4000
LL <- rep(0,n)
for(i in seq_len(n)){
	jjstar <- sample(jury)
	names(jjstar) <- names(jury)
	LL[i] <- loglik(indep(eurodance_maxp),ordervec2supp(jjstar),log=FALSE)
}
```

```{r,label=comparelogliks}
plot(sort(LL),log="y")
p <- loglik(indep(eurodance_maxp),ordervec2supp(jury),log=FALSE)
abline(h=p)
```

```{r,label=sumll}
sum(LL[LL<p])/sum(LL)
```
